Time Series Bootstrapping For Solar Current

### 2021-12-08 deliverables/paper.Rmd
Added images subdirectory and preliminary figure saving

```{r libs}
library(tidyverse)
```

@@

block_bootstrap_estimates_from_df <- function(df, B=10000) {
  block_bootstrap_estimates <- rep(NA, B)
  blocks <- make_blocks_from_df(df)
  number_of_blocks <- nrow(blocks)
  for (i in 1:B) {
    # sample blocks
    idx <- sample(1:number_of_blocks, number_of_blocks, replace = TRUE)
    # Concatenate blocks at the given indices
    # This gives a "pseudo-dataset" containing resampled blocks
    block_bootstrap_estimates[i] <- median(as.vector(t(blocks[idx, ])))
  }
  return(block_bootstrap_estimates)
}
test_est <- block_bootstrap_estimates_from_df(df_high_irradiance)

@@

iid_bootstrap_estimates_from_df <- function(df, B=10000) {
  boot_current <- boot(df$current_out, medianv, B)
  return(boot_current$t)
}

@@

ggplot() +
  geom_histogram(aes(x = test_est),color="red",alpha=0.5) +
  geom_histogram(aes(x = test_iid),color="blue",alpha=0.5) +
  theme_bw()

np <- function(x, l) {
  n <- length(x)
  print(n)
  # l <- n %/% b
  # b <- n %/% l
  b <- floor(n / l)
  print(b)
  print(n / b)
  blocks <- matrix(NA, nrow = b, ncol = l)
  for (i in 1:b) {
    # blocks[i, ] <- x[(i - 1) * l + 1:(i * l)]
    print(x[(i - 1) * l + 1:(i * l)])
  }
  return(blocks)
}

nbb <- function(x, l) {
  B <- 10000
  b <- floor(length(x) / l)
  theta_hat_star_nbb <- rep(NA, B)
  # nb_blocks <- np(x, l, b)
  nb_blocks <- np(x, l)
  for (i in 1:B) {
    # sample blocks
    idx <- sample(1:b, b, replace = TRUE)
    theta_hat_star_nbb[i] <- mean(x[idx, ])
  }
  ggplot() +
    geom_histogram(aes(theta_hat_star_nbb))

  st.d <- sd(theta_hat_star_nbb)
  bias <- mean(theta_hat_star_nbb) - mean(x)

  print(paste(
    "The standard deviation with ", l, " blocks is: ", st.d, ". \n The bias is: ",
    bias
  ))
}
```

@@

nbb(hours, 4) # in order to make b blocks I would need to solve for b = [n/l] (floor) where n is the length of our data and l is 4, so make nbb call l instead of b

nbb(hours, 12)

# Could also block instead by hours but by total current output. Peak hours would be a frame around the highest output and then hours before and after would coincide with that. This would cause the hours to potentially be different based on the season/month as months that get dark earlier could see peak hours earlier in the day.

>>>>

```{r libs}
library(tidyverse)
library(boot)
```

@@

block_bootstrap_estimates_from_df <- function(df, B = 10000) {
  block_bootstrap_estimates <- rep(NA, B)
  blocks <- make_blocks_from_df(df)
  number_of_blocks <- nrow(blocks)
  for (i in 1:B) {
    # sample blocks
    idx <- sample(1:number_of_blocks, number_of_blocks, replace = TRUE)
    # Concatenate blocks at the given indices
    # This gives a "pseudo-dataset" containing resampled blocks
    block_bootstrap_estimates[i] <- mean(as.vector(t(blocks[idx, ])))
  }
  return(block_bootstrap_estimates)
}
test_est <- block_bootstrap_estimates_from_df(df_high_irradiance)

@@

iid_bootstrap_estimates_from_df <- function(df, B = 10000) {
  boot_current <- boot(df$current_out, meanv, B)
  return(boot_current$t)
}

@@

mean_samp_dist <- ggplot() +
  geom_histogram(aes(x = test_est), color = "red", alpha = 0.5) +
  geom_histogram(aes(x = test_iid), color = "blue", alpha = 0.5) +
  theme_bw()
ggsave("./images/mean_samp_dist.png", mean_samp_dist)
```

@@

# nbb(hours, 4) # in order to make b blocks I would need to solve for b = [n/l] (floor) where n is the length of our data and l is 4, so make nbb call l instead of ib

# nbb(hours, 12)

# Could also block instead by hours but by total current output. Peak hours
# would be a frame around the highest output and then hours before and after
# would coincide with that. This would cause the hours to potentially be
# different based on the season/month as months that get dark earlier could see
# peak hours earlier in the day.
